Two years of CiTO annotations

### 2022-11-13 article.Rmd
Tweaking references in links

The *Journal of Cheminformatics* template is available from the journal's GitHub organization, and authors and editors should feel free to adapt it to the needs of other journals. The BioHackrXiv (https://biohackrxiv.org/) preprint server also support CiTO annotations [@cito:citesAsDataSource:Prins2021] and this template can be found at https://github.com/biohackrxiv/publication-template.

@@

Because many publishing platforms currently do not support display of citation level intention annotation,
the default model only provides the annotation in the bibliography. The choice was made to use the `bibnotes`
idea which allows giving additional notes to a reference in the bibliography. The CiTO Pilot uses
the *safe CURIE* standard proposed by the W3C in 2010 [@usesMethodIn:BirBeck2010]. The Markdown templates
implement this idea. However, typesetting in the *Journal of Cheminformatics* has shown to be inconsisten,
even within single articles, suggesting additional training or guidance could be needed.

@@

LaTeX users may find them in a situation between that of Markdown users and reference manager users:
only if a manuscript-level Bib(La)TeX file is used the CiTO annotation can be added as notes to the
BiBTeX file. This is explained in this guidance document: https://jcheminform.github.io/jcheminform-author-guidelines/cito-guidelines/latex.html.

@@

#### Availability of data and materials
CiTO annotation in the *Journal of Cheminformatics* are available from the journal's articles. CiTO
annotation data in Scholia is available from [Wikidata](https://wikidata.org/). Markdown templates that
support CiTO are available from https://github.com/jcheminform/markdown-jcheminf and
https://github.com/biohackrxiv/publication-template.

#### Competing interests
Text for this section.

#### Funding
Part of this work was supported by ELIXIR, the research infrastructure for life-science data.

#### Authors' contributions
Text for this section.

#### Acknowledgements

>>>>

The *Journal of Cheminformatics* template is available from the journal's GitHub organization, and authors and editors should feel free to adapt it to the needs of other journals. The BioHackrXiv ([https://biohackrxiv.org/](https://biohackrxiv.org/))
preprint server also support CiTO annotations [@citesAsDataSource:Prins2021] and this template can be found at
[https://github.com/biohackrxiv/publication-template](https://github.com/biohackrxiv/publication-template).

@@

Because many publishing platforms currently do not support display of citation level intention annotation,
the default model only provides the annotation in the bibliography. The choice was made to use the `bibnotes`
idea which allows giving additional notes to a reference in the bibliography. The CiTO Pilot uses
the *safe CURIE* standard proposed by the W3C in 2010 [@usesMethodIn:McCarron2010]. The Markdown templates
implement this idea. However, typesetting in the *Journal of Cheminformatics* has shown to be inconsisten,
even within single articles, suggesting additional training or guidance could be needed.

@@

LaTeX users may find them in a situation between that of Markdown users and reference manager users:
only if a manuscript-level Bib(La)TeX file is used the CiTO annotation can be added as notes to the
BiBTeX file. This is explained in this guidance document:
[https://jcheminform.github.io/jcheminform-author-guidelines/cito-guidelines/latex.html](https://jcheminform.github.io/jcheminform-author-guidelines/cito-guidelines/latex.html).

@@

### Availability of data and materials

CiTO annotation in the *Journal of Cheminformatics* are available from the journal's articles. CiTO
annotation data in Scholia is available from [Wikidata](https://wikidata.org/). Markdown templates that
support CiTO are available from
[https://github.com/jcheminform/markdown-jcheminf](https://github.com/jcheminform/markdown-jcheminf) and
[https://github.com/biohackrxiv/publication-template](https://github.com/biohackrxiv/publication-template).

### Competing interests

No competing interests.

### Funding

Part of this work was supported by ELIXIR, the research infrastructure for life-science data.

### Authors' contributions

Not applicable.

### Acknowledgments
